Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-15 thesis/results.tex
Remove section on random tree, can't find much info about this algorithm, suspect it's just another version of random forest
More detail in conclusion

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

\subsection{Random Tree}

@@

The real Tor network consists of over two hundred thousand computer systems,
with over two thousand routers \parencite{TorStatus:2011fk}, all with different
operating systems, different hardware, different configurations and available
bandwidth. All the variables that were controlled for during this experiment
are present in the real network, and may be amplified by it's greater size.
Without further research it is difficult to say if the technique demonstrated
here will apply in the wild.

@@

\begin{enumerate*}
  \item{Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?}

@@

  \item{Can Tor traffic be identified using automated matching techniques?}

@@

    The value of this level of accuracy depends on the application. Identifying
    multiple regular connections to the Tor network may provide sufficient
    confidence to classify a system as a Tor node. This could be combined with
    other known properties of the Tor network to increase confidence.

  \item{Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?}

@@

\end{enumerate*}

@@

Using Tor as a communications proxy incurs some overhead, sufficient enough that
when using a Tor proxy in controlled conditions, Tor traffic can be
distinguished from regularly encrypted traffic. This overhead may be sufficient
enough that Tor nodes in a real world network can be identified by using readily
available eavesdropping techniques.

However, this experiment was based on a small set of simulated data, with which
it would be impossible to cover all the possible real world conditions. The
variability present in the real Tor network may make this classification
technique impossible. Further research needs to be conducted with live packet
traces from real participants in the Tor network.

>>>>

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

@@

The real Tor network consists of over two hundred thousand computer systems,
with over two thousand routers \parencite{TorStatus:2011fk}, all with different
operating systems, different hardware, different configurations and available
bandwidth. All the variables that were controlled for during this experiment
are present in the real network, and may be amplified by it's greater size.

Real world traffic may produce completely different statistical properties.
This could simply mean that new features should be selected to create a real
world Tor classifier, or it could mean that there is too much variability
present for modern classification algorithms. The AdaBoost algorithm for
instance, has shown to be defeated by the presence of random noise which would
be more likely in an real environment \parencite{Long:2008ha}.

Without further research it is difficult to say if the technique demonstrated
here will apply in the wild.

@@

\subsection{Can Tor traffic be distinguished from other network traffic that
uses similar or the same encryption and protocols?}

@@

\subsection{Can Tor traffic be identified using automated matching techniques?}

@@

The value of this level of accuracy depends on the application. A
commercial Internet Service Provider (ISP) or University network may risk
upsetting its users if it were to accidentally block 5\% of regular
encrypted traffic by implementing a firewall that blocked based on this
classifier. Alternatively it could prove useful for identifying systems
running the Tor software. Tor nodes make multiple connections to the
network, both in parallel and over time. Recognizing several Tor streams to
an individual system would provide sufficient confidence to classify it as
a Tor node.

\subsection{Does Tor traffic have characteristics that make it readily
distinguishable using heuristics based matching?}

@@

@@

Using Tor as a communications proxy incurs some overhead, sufficient enough
that when using a Tor proxy in controlled conditions, its traffic can be
distinguished from regularly encrypted traffic. This overhead may be sufficient
enough that Tor nodes in a real world network can be identified by using
readily available eavesdropping techniques.

However, this experiment was based on a small set of simulated data, with which
it would be impossible to cover all possible real world conditions. The
variability and noise present in the real Tor network may make this
classification technique impossible.

Further research needs to be conducted with live packet traces from real
participants in the Tor network. Most existing traffic classification research
operates this way, using exact matching techniques to separate traces collected
into treatment and control groups. Real Tor traffic might be captured from
publicly available and co-operating Tor nodes and compared to real encrypted
sessions between well known public HTTPS servers.
